Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-20 chapters/whenwhere/paper.tex
add time estimation related work
constraint functions

Outdoor images often contain sufficient visual information to
understand geographic information about the scene, such as where the
image was captured. Developing effective algorithms for this task has
received significant attention for many years~\cite{im2gps,planet}.
The appearance of an outdoor scene can also change rapidly. These
changes are often due to fleeting, or transient, attributes such as
lighting and weather conditions, that dramatically affect the visual
perception of an environment. For instance, consider a scene that
changes from sunny and pleasant to rainy and brooding in mere minutes.
Several methods have been proposed for automatically understanding and
extracting these subtle characteristics from
imagery~\cite{patterson2012sun,lu2014two,laffont2014transient,baltenberger16transient}.
Estimating these types of transient attributes has importance in a
number of fields, including: environmental
monitoring~\cite{wang2013observing,fedorov2014snow}, as a
pre-processing step for
calibration~\cite{jacobs13cloudcalibration,workman2014rainbow}, and
enabling semantic browsing of large photo
collections~\cite{jacobs07amos,laffont2014transient}. Our work fuses these two
research areas by learning to estimate geo-temporal image features,
which are related to when and where an image was captured.

@@

Other work has explored how to estimate the time that an image was
captured. Salem et al.~\cite{salem2016dating} demonstrate that human
appearance, including clothing and hairstyle, is a useful cue for
dating images. Matzen and Snavely predict timestamps for photos by
matching against a time-varying reconstruction of a scene.  Volokitin
et al.~\cite{eth_biwi_01292} use representations extracted from CNNs
to estimate ambient temperature and time of year for outdoor images.
In our work we explore how location and time estimation can be used
as tasks for learning geo-temporal features.

>>>>

In this chapter, we focus on developing the constraint function for 
the capture time and the camera location for outdoor images.
Outdoor images often contain sufficient visual information to
understand geographic information about the scene, such as where the
image was captured. Developing effective algorithms for this task has
received significant attention for many years~\cite{im2gps,planet}.
The appearance of an outdoor scene can also change rapidly. These
changes are often due to fleeting, or transient, attributes such as
lighting and weather conditions, that dramatically affect the visual
perception of an environment. For instance, consider a scene that
changes from sunny and pleasant to rainy and brooding in mere minutes.
Several methods have been proposed for automatically understanding and
extracting these subtle characteristics from
imagery~\cite{patterson2012sun,lu2014two,laffont2014transient,baltenberger16transient}.
Estimating these types of transient attributes has importance in a
number of fields, including: environmental
monitoring~\cite{wang2013observing,fedorov2014snow}, as a
pre-processing step for
calibration~\cite{jacobs13cloudcalibration,workman2014rainbow}, and
enabling semantic browsing of large photo
collections~\cite{jacobs07amos,laffont2014transient}. Our work fuses these two
research areas by learning to estimate geo-temporal image features,
which are related to when and where an image was captured.

@@

Other work has explored how to estimate the time that an image was
captured. Salem et al.~\cite{salem2016dating} demonstrate that human
appearance, including clothing and hairstyle, is a useful cue for
dating images. Matzen and Snavely~\cite{matzen2014scene} predict timestamps for photos by
matching against a time-varying reconstruction of a scene.  Volokitin
et al.~\cite{eth_biwi_01292} use representations extracted from CNNs
to estimate ambient temperature and time of year for outdoor images.
In our work we explore how location and time estimation can be used
as tasks for learning geo-temporal features.
